### 2019-05-16 manuscript/response.tex

\begin{quote}
Line 133: Replace ``and polyploid populations'' by ``in polyploid populations''?
\end{quote}

Fixed.

\begin{quote}
Line 133-135: Should probably move this information in the intro.
\end{quote}

We now explain the effect of polyploidization on self-incompatibility more thoroughly in the Introduction.

@@

\begin{quote}
Line 152: It would be useful to refer to the figures that illustrate the models in the methods.
It would help to understand them.
\end{quote}

Fixed. % TODO

\begin{quote}
Line 360: ``Simultaneous consideration of breeding system'' and what?
Polyploidy, hidden state?
The sentence is not clear
\end{quote}

\begin{quote}
Line 363: ``These results indicate that some of the effects of a hidden trait can be explained by each of the two traits under consideration''.
Not sure I understand this sentence. Is it possible to clarify?
\end{quote}

Reworded.

\begin{quote}
Line 380: The authors should explain in more details the link between the breakdown of SI and the evolution of gender dimorphism.
\end{quote}

We added a brief explanation.

### 2019-05-16 manuscript/discussion.tex
fixed up small points from reviewer 2

Previous analyses of the effects of ploidy on diversification showed that diploids had greater net diversification rates than polyploids across multiple clades of the angiosperm phylogeny \citep{mayrose_2011, mayrose_2015}. 
We obtain a broadly similar outcome when considering only the effects of ploidy, but the results change significantly with joint consideration of hidden states and breeding systems (\cref{figure:netdivall}A and B). 
The addition of a hidden trait blurs differences in diversification rates between diploids and polyploids.
Simultaneous consideration of breeding system better explains the variation of the inferred net diversification rates among ploidy states. 
SI, which is itself associated with a faster diversification rate, is the breeding system context in which many diploids occur.
Among SC species, diploids and polyploids are associated with similar diversification rates (\cref{figure:netdivall}E).
These results indicate that some of the effects of a hidden trait can be explained by each of the two traits under consideration. 
The finding thus demonstrates how the relative influence of two traits on diversification can be disentangled in a comparative phylogenetic framework.

@@

We find that SI diploid lineages are much more likely to take a one-step  ID$\rightarrow$CP pathway to polyploidy rather than a two-step ID$\rightarrow$CD$\rightarrow$CP pathway, in Solanaceae.
This result is significant because it has a number of implications for the inference of history of breeding and sexual systems in flowering plants.
First, support for the direct pathway lends credence to the idea that breakdown of SI by WGD---by generation of diploid `heteroalleleic' pollen---may often trigger the evolution of gender dimorphism across angiosperms \citep{miller_2000}.
A more direct and definitive test of this hypothesis would additionally examine the propensity of polyploids generated through either pathway to become dioecious \citep{robertson_2011}.
Second, statistical phylogenetic approaches measure lineage transition rates.
Transitions depend on a combination of availability of individual mutation rates, which generate trait variation, and selection, which may cause disproportionate loss or fixation of these mutants.
Estimates of mutation rates are highly uncertain, but the total rate of breakdown of SI within diploids ranges is estimated to be on the order of  $\mu_{IC} = 10^{-5}$ per pollen grain, and includes breakdown by tetraploidization \citep{lewis1979}, which is itself estimated to occur on the order of $\mu_{DP} = 10^{-5}$ \citep{ramsey_1998}. 
Seemingly, then, the simple genic mutation rate that leads to loss of SI is at best equal to tetraploidization mutation rate, and possibly far lower.
We nevertheless recover transition rates from ID to CD ($q_{IC}$) threefold greater than $\rho_{I}$, indicating that selection restricts the fixation rate of new polyploids compared with new SC mutants \citep{robertson_2011}.
Overall, our findings suggest that the effect of ploidy is largely explained explained by its correlation with breeding system, and that other unknown factors work with breeding system to determine diversification rates.

>>>>

Previous analyses of the effects of ploidy on diversification showed that diploids had greater net diversification rates than polyploids across multiple clades of the angiosperm phylogeny \citep{mayrose_2011, mayrose_2015}. 
We obtain a broadly similar outcome when considering only the effects of ploidy, but the results change significantly with joint consideration of hidden states and breeding systems (\cref{figure:netdivall}A and B). 
The addition of a hidden trait blurs differences in diversification rates between diploids and polyploids.
The model with breeding system also included better explains the variation of the inferred net diversification rates among ploidy states. 
SI, which is itself associated with a faster diversification rate, is the breeding system context in which many diploids occur.
Among SC species, diploids and polyploids are associated with similar diversification rates (\cref{figure:netdivall}E).
These results indicate that the hidden trait in the analysis of one focal trait can in part be explained by the other focal trait.
The finding thus demonstrates how the relative influence of two traits on diversification can be disentangled in a comparative phylogenetic framework.

@@

We find that SI diploid lineages are much more likely to take a one-step  ID$\rightarrow$CP pathway to polyploidy rather than a two-step ID$\rightarrow$CD$\rightarrow$CP pathway, in Solanaceae.
This result is significant because it has a number of implications for the inference of history of breeding and sexual systems in flowering plants.
First, support for the direct pathway lends credence to the idea that breakdown of SI by WGD---by generation of diploid `heteroalleleic' pollen---may often trigger the evolution of gender dimorphism across angiosperms, as a different mechanism of inbreeding avoidance \citep{miller_2000}.
A more direct and definitive test of this hypothesis would additionally examine the propensity of polyploids generated through either pathway to become dioecious \citep{robertson_2011}.
Second, statistical phylogenetic approaches measure lineage transition rates.
Transitions depend on a combination of availability of individual mutation rates, which generate trait variation, and selection, which may cause disproportionate loss or fixation of these mutants.
Estimates of mutation rates are highly uncertain, but the total rate of breakdown of SI within diploids ranges is estimated to be on the order of  $\mu_{IC} = 10^{-5}$ per pollen grain, and includes breakdown by tetraploidization \citep{lewis1979}, which is itself estimated to occur on the order of $\mu_{DP} = 10^{-5}$ \citep{ramsey_1998}. 
Seemingly, then, the simple genic mutation rate that leads to loss of SI is at best equal to tetraploidization mutation rate, and possibly far lower.
We nevertheless recover transition rates from ID to CD ($q_{IC}$) threefold greater than $\rho_{I}$, indicating that selection restricts the fixation rate of new polyploids compared with new SC mutants \citep{robertson_2011}.
Overall, our findings suggest that the effect of ploidy on lineage diversification rate is largely explained by its correlation with breeding system, and that other unknown factors work with breeding system to determine diversification rates.

### 2019-05-16 manuscript/introduction.tex
fixed up small points from reviewer 2

Here, we examine the roles of ploidy and breeding system, as well as their interaction, on the diversification process in Solanaceae.
Using extensive trait data, and considering other possible sources of heterogeneity in the diversification process, we assess the influence of these traits on speciation and extinction rates.
First, we present models in which the effect of ploidy and breeding system are considered separately, and we compare the inferences to previously published results. 
Second, we add a hidden trait to each of those models and investigate whether the focal trait still explains differences in diversification.
Third, we model ploidy and breeding system jointly to assess their combined relationship to diversification, with or without an additional hidden trait.
With this joint trait model, we also quantify the relative contributions of the two pathways from SI diploids to SC polyploids.
For all of the models involving ploidy, we investigate the potential effects of including diploidization.
Our results highlight the importance of considering non-additive effects of traits on net diversification rates, especially when there are strong biologically driven correlations among them.

>>>>

Here, we examine the roles of ploidy and breeding system, as well as their interaction, on the diversification process in Solanaceae.
Importantly, our analyses aim to parse out the associations of these two traits on speciation and extinction rates while simultaneously allowing that other processes could influence diversification as well.
First, we present models in which the effect of ploidy and breeding system are considered separately, and we compare the inferences to previously published results. 
Second, we add a hidden trait to each of those models and investigate whether the focal trait still explains differences in diversification.
Third, we model ploidy and breeding system jointly to assess their combined relationship to diversification, with or without an additional hidden trait.
With this joint trait model, we also quantify the relative contributions of the two pathways from SI diploids to SC polyploids.
For all of the models involving ploidy, we investigate the potential effects of including diploidization.
Our results highlight the importance of considering non-additive effects of traits on net diversification rates, especially when there are strong biologically driven correlations among them.
